Efficient ancestry and mutation simulation with msprime 1.0

### 2021-08-09 paper.tex
updadet acknowls

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Department of Biology and Institute of Ecology and Evolution,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{FIXME: THIBAUT's AFFILIATION}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{FIXME: JERE'S AFFILIATION}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
BE was supported by  DFG grant  273887127 through Priority
Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research
Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.

>>>>

% Bjarki
\affil[8]{Leibniz Institute for Evolution and Biodiversity
Science, Museum f\"ur Naturkunde Berlin }
% Castedo
\affil[9]{FIXME: CASTEDO's AFFILIATION}
% Jared, Murillo, Peter, Andy
\affil[10]{Department of Biology and Institute of Ecology and Evolution,
    University of Oregon}
% Ariella
\affil[11]{Department of Genetics, University of North Carolina at Chapel Hill}
% Gregor
\affil[12]{The Roslin Institute and Royal (Dick) School of Veterinary Studies,
    University of Edinburgh}
% Bing
\affil[13]{FIXME: BING's AFFILIATION}
% Winni
\affil[14]{FIXME: WINNI's AFFILIATION}
% Simon, Dom, Ivan
\affil[15]{Department of Human Genetics, McGill University}
% Michael
\affil[16]{FIXME: MICHAEL's AFFILIATION}
% Nathaniel
\affil[17]{FIXME: NATHANIEL's AFFILIATION}
% Consuelo
\affil[18]{National Laboratory of Genomics for Biodiversity (LANGEBIO),
    Unit of Advanced Genomics, CINVESTAV, Irapuato, Mexico}
% Saunack
\affil[19]{FIXME: SAUNACK's AFFILIATION}
% Thibaut
\affil[20]{Professorship for Population Genetics, Department of Life Science Systems, Technical University of Munich}
% Kevin
\affil[21]{Ecology and Evolutionary Biology, University of California at Irvine}
% Hugo
\affil[22]{FIXME HUGO's AFFILIATION}
% Jere
\affil[23]{Department of Statistics, University of Warwick}
% Peter (second affil)
\affil[24]{Department of Mathematics, University of Oregon}

@@

\section*{Acknowledgements}
JK is supported by the Robertson Foundation.
Jere Koskela is supported in part by EPSRC grant EP/R044732/1.
ADK was supported by NIH awards R01GM117241 and R01HG010774.
Franz Baumdicker is funded by the Deutsche Forschungsgemeinschaft
EXC 2064/1 -- Project number 390727645, and EXC 2124 -- Project number 390838134.
Graham Gower was supported by a Villum Fonden Young Investigator award to Fernando Racimo (project no. 00025300).
BE was supported by  DFG grant  273887127 through Priority
Programme SPP 1819: Rapid Evolutionary Adaptation (grant STE 325/17-2) to Wolfgang Stephan; BE would also like to acknowledge  funding through The Icelandic Research
Centre (Rann{\'i}s) through an Icelandic Research Fund Grant of  Excellence nr.\ 185151-051 to Einar \'Arnason,  Katr\'in Halld\'orsd\'ottir,  Alison Etheridge,  Wolfgang Stephan, and BE.
Gregor Gorjanc is supported by the Chancellor's Fellowship of the University of
Edinburgh and the BBSRC grant to The Roslin Institute BBS/E/D/30002275.
